\textbf{NBA Party}

### 2017-07-15 cardinal_analytx_presentation/nightlife_and_sports.tex
Changed where figures are read from.

\begin{frame}
  \centering   \includegraphics[scale=0.55]{../writing/meet_the_spread} 
\end{frame}

@@

\begin{frame}   \frametitle{Overzealous assumption: next day opponent uncorrelated}
  \centering \includegraphics[scale=0.25]{../writing/next_day_opponent} 
\end{frame}

\begin{frame}   \frametitle{A closer look at NBA games on the road}
  \centering \includegraphics[scale=0.25]{../writing/next_day_opponent_on_tour} 
\end{frame}

@@

\begin{frame}   
  \frametitle{Travel distance comparison}
  \centering \includegraphics[scale=0.25]{../writing/travel_dist_density_by_party} 
\end{frame}

@@

\begin{frame}   
  \frametitle{Continuous measure of party}
  \centering \includegraphics[scale=0.375]{../writing/Party_by_Team_Location} 
\end{frame}

@@

% \begin{frame}   
%   \frametitle{Continuous measure of party (MLB)}
%   \centering \includegraphics[scale=0.3]{../writing/Party_by_Team_Location_mlb}   
% \end{frame}

@@

\begin{frame}   \frametitle{Betting in MLB}
  \centering
  \includegraphics[scale=0.5]{../writing/mlb_bets_by_season} \end{frame}

@@

\begin{frame}
  \centering
  \includegraphics[scale=0.25]{../writing/distribution_point_spreads_nba}
\end{frame}

@@

\begin{frame}   \frametitle{Why \# drinking establishments or population won't work}
  \includegraphics[scale=0.3]{../writing/why_drinks_or_population_dont_work} \end{frame}

>>>>

\begin{frame}
  \centering   \includegraphics[scale=0.55]{meet_the_spread} 
\end{frame}

@@

% \begin{frame}   \frametitle{Overzealous assumption: next day opponent % uncorrelated}
%   \centering \includegraphics[scale=0.25]{next_day_opponent} 
% \end{frame}

\begin{frame}   \frametitle{A closer look at NBA games on the road}
  \centering \includegraphics[scale=0.25]{next_day_opponent_on_tour} 
\end{frame}

@@

\begin{frame}   
  \frametitle{Travel distance comparison}
  \centering \includegraphics[scale=0.25]{travel_dist_density_by_party} 
\end{frame}

@@

\begin{frame}   
  % \frametitle{Continuous measure of party}
  \hspace*{-25pt}
  \includegraphics[scale=0.275]{Party_by_Team_Location} 
\end{frame}

@@

% \begin{frame}   
%   \frametitle{Continuous measure of party (MLB)}
%   \centering \includegraphics[scale=0.3]{Party_by_Team_Location_mlb}   
% \end{frame}

@@

\begin{frame}   \frametitle{Betting in MLB}
  \centering
  \includegraphics[scale=0.25]{mlb_bets_by_season} \end{frame}

@@

\begin{frame}
  \centering
  \includegraphics[scale=0.25]{distribution_point_spreads_nba}
\end{frame}

@@

\begin{frame}   
  % \frametitle{Why \# drinking establishments or population won't work}
  \includegraphics[scale=0.25]{why_drinks_or_population_dont_work} \end{frame}
